% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Hao Meng}

\basicInfo{
  \email{hmeng1@stevens.edu} \textperiodcentered\ 
  \phone{(646) 883-9966} \textperiodcentered\ 
  \linkedin[billryan8]{https://www.linkedin.com/in/billryan8}}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Stevens Institute of Technology}, Hoboken, NJ}{2016 -- Present}
\textit{Master student} in Computer Science (CS), expected March 2018
\datedsubsection{\textbf{Heilongjiang University}, Heilongjing, China}{2012 -- 2016}
\textit{B.S.} in Software Engineering (SE)
\textit{B.S.} in Finance (F)

\section{\faUsers\ Experience}
\datedsubsection{\textbf{DunAn Precision, INC} Austin, TX}{June. 2017 -- Aug. 2017}
\role{Summer Intern}{Manager: Rachel Chang}
Participated at a 7-member startup team as a Technical Consultant. Assisted and advised team members in technological problems.
\begin{itemize}
  \item Collected customer requirements and designed prototype, implemented corporate web applications which include a company website and an online shop.
  \item Integrated the Django framework, and implemented all the Controller in MVC framework.
  \item Designed effective product search, implemented Ajaxified cart and dynamic adding, deleting functions.
  \item Linked the Braintree Payments Integration which can pay by PayPal.
  \item Registered a domain name and deployed the Django Application to Pythonanywhere.
\end{itemize}

\datedsubsection{\textbf{Tiny URL Website Design}}{Oct. 2017 -- Dec. 2017}
\role{JavaScript, HTML, Angular.js, Boorstrap}{Individual Projects, collaborated with Xian Zhang}
Developed a web application with a shortened target URL while evaluating site visit traffic analysis.
\begin{itemize}
  \item Stored the conversion method of long URL to short URL into MongoDB/Mongoose.
  \item Decrease response time by building cache after analyzing client demand.
\end{itemize}

\datedsubsection{\textbf{Predicting Airbnb Housing Prices In London}}{Jan. 2017 -- May. 2017}
\role{Python, Pandas, Numpy}{Individual Projects}
\begin{itemize}
  \item Collected non-commercial data which contains 42,646 records scarped from open Airbnb listing.
  \item Cleaned the data by removing irrelevant and suspect records, converted them into desired format.
  \item Performed exploratory data analysis which includes shapes of distributions, correlation matrix of predictors.
  \item Built baseline model to predicts the housing prices based on Room Type and Neighborhood.
  \item Built and evaluated advanced models inlude Liner Regression, Random Forest.
\end{itemize}

\datedsubsection{\textbf{Machine Learning Algorithms for Trading}}{Oct. 2017 -- Dec. 2017}
\role{Python, Pandas, Numpy}{Individual Projects}
\begin{itemize}
  \item Studied the characteristics of daily stock time series, implemented the technical analysis indicators pool.
  \item Selected appropriate indicators by back testing, implemented linear regression, KNN and bootstrap aggregating by Python instead of calling library.
  \item Established initial forecast models based on the above algorithms, use them to predict the futures prices.
  \item Built Trading Strategies on the constituent stocks of S/&P 500 Index of 2008-2012, and evaluated the performance of the portfolio. The number of profitable stocks is 389 which is 64.8% of the total.
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Java == Python > C++ > C
  \item Platform: Linux
  \item Development: Web, Data Analysis
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{the Master's Fellows Program}, Award on Award for the 2016 Fall Graduate semester }{Jun. 2016}

% \section{\faInfo\ Miscellaneous}
% \begin{itemize}[parsep=0.5ex]
%   \item Blog: http://your.blog.me
%   \item GitHub: https://github.com/username
%   \item Languages: English - Fluent, Mandarin - Native speaker
% \end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
